Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-17 content/impl.tex
restating lemma
sorting citations; adding efficiency lemma and proof

\otodo{Sagiv et al. define a notion of an ``efficient'' implementation of micro-functions.
    If the micro-functions are ``efficient'', then the asymptotic complexity bounds proven by
    Sagiv hold. Our implementation is ``efficient'' if we assume that the number of correlated
    receivers is a constant independent of the size of the program. That seems a stretch. If
    it's linear in the size of the program, then we would need to add a factor to their complexity
    bounds. Their bound is $O(ED^3)$, while ours would be $O(ED^3R)$. But then we can't directly use their complexity proof; we would have to adapt it.
    I'm leaning towards leaving out any mention of ``efficient'' implementation.}

@@

\begin{lemma}\label{lem:onlycorrrec}
  Let $P$ be an IFDS problem. Then
  \begin{equation}
    \backCC\left(\resultIDE\left(\transCC_\rcc(P)\right)\right)=\backCC(\resultIDE\left(\transCC_R(P)\right))\,.
  \end{equation}
\end{lemma}

>>>>

\subsection{Efficiency}
\otodo{Sagiv et al. define a notion of an ``efficient'' implementation of micro-functions.
    If the micro-functions are ``efficient'', then the asymptotic complexity bounds proven by
    Sagiv hold. Our implementation is ``efficient'' if we assume that the number of correlated
    receivers is a constant independent of the size of the program. That seems a stretch. If
    it's linear in the size of the program, then we would need to add a factor to their complexity
    bounds. Their bound is $O(ED^3)$, while ours would be $O(ED^3R)$. But then we can't directly use their complexity proof; we would have to adapt it.
    I'm leaning towards leaving out any mention of ``efficient'' implementation.}
As defined in~Sagiv et al.~\cite{sagiv1996precise}, a representation of micro functions is efficient if the following conditions hold:
\begin{enumerate}
	\item There is a representation for the identity and top functions.
  \item The representation is closed under the meet and composition operations.
  \item The micro functions form a finite-height lattice.
  \item The apply, meet, composition, and equality-check operations can be computed in constant time.
  \item There is a constant bound on the storage space for a micro function representation.
\end{enumerate}
\begin{restatable}{lemma}{efficient}\label{lem:efficient}
  The correlated-call representation of a micro function is efficient.
\end{restatable}

@@

\begin{restatable}{lemma}{onlycorrrec}\label{lem:onlycorrrec}
  Let $P$ be an IFDS problem. Then
  \begin{equation}
    \backCC\left(\resultIDE\left(\transCC_\rcc(P)\right)\right)=\backCC(\resultIDE\left(\transCC_R(P)\right))\,.
  \end{equation}
\end{restatable}
